Skin Lesion Classification on Imbalanced Data Using Deep Learning with Soft Attention

### 2022-10-03 MDPI/sensors-1915564-redo - For Proof/sensors-1915564.tex
Update Paper Final Version

\address{$^{1}$ \quad \hl{School} %MDPI: we combined the same affiliation 1 and 3, please confirm.
 of Electrical and Electronic Engineering, Hanoi University of Science and Technology, \hl{Vietnam;} %MDPI: Please add the city and post code.
\hl{ khoi.dh200322@sis.hust.edu.vn} %MDPI: This email address is different from the submitting system. Please confirm which one is correct.
\\
$^{2}$ \quad Faculty of Information Technology, University of Transport and Communications, \hl{Vietnam} %MDPI: Please add the city and post code.
}

@@

% Abstract (Do not insert blank lines, i.e. \\) s
\abstract{Today, the rapid development of industrial zones leads to an increased incidence of skin	diseases because of polluted air. According to a report by the American Cancer Society, it is estimated that in 2022 there will be about 100,000 people suffering from skin cancer and more than 7600 of these people will not survive. In the context that doctors at provincial hospitals and health facilities are overloaded, doctors at lower levels lack experience, and having	a tool to support doctors in the process of diagnosing skin diseases quickly and accurately is essential. Along with the strong development of artificial intelligence technologies, many solutions to support the diagnosis of skin diseases have been researched and developed. In this paper, a combination of one Deep Learning model (DenseNet, InceptionNet, ResNet, etc) with Soft-Attention, which unsupervisedly extract a heat map of main skin lesions. Furthermore, personal information including age and gender are also used. It is worth noting that a new loss function that takes into account the data imbalance is also proposed. Experimental results on data set HAM10000 show that using InceptionResNetV2 with Soft-Attention and the new loss function gives 90 percent accuracy, mean of precision, f1-score, recall-score, and AUC scores of 0.81, 0.81, 0.82, and 0.99, respectively. Besides, using MobileNetV3Large combined with Soft-Attention and the new loss function, even though the number of parameters is 11~times less and the number of hidden layers is 4 times less, it achieves an accuracy of 0.86 and 30 times faster diagnosis than InceptionResNetV2.}

@@

	To adapt the rise in skin cancer cases, AI algorithms over the last decade has a great performance. Some typical models that can be mentioned are DenseNet \cite{06993}, EfficientNet~\cite{04861}, Inception \cite{00567}\hl{\mbox{\cite{07261}}}, MobileNets\cite{04861,04381,02244}, \hl{Xception\mbox{\cite{02357}}}, ResNet \cite{03385,05027}, and NasNet \cite{07012}. Some of these models which have been used as a backbone model in this paper will be discussed in the Related Work section.

@@

	{Skin lesion classification is not a new area, since there are many great performance models constructed, recent years. The skin classification approaches can be divided into two main approaches: Deep Learning and Machine Learning. Both approaches gain great performance. Data Augmentation and Feature Extractor, otherwise are two main supporters that make the model better.
		\begin{table}[H]
\caption{\hl{Related} %MDPI: we updated the format of all tables, please confirm the change. Please cite the table in the text and ensure the first citation of each table appears in numerical order.
 Works Summary.}
\label{table:related-work-summary}

\begin{adjustwidth}{-\extralength}{0cm}
%\centering %% If there is a figure in wide page, please release command \centering
\centering
\begin{tabular}{ c  p{1.8cm}  p{1.8cm}  p{2.55cm}  p{1.5cm}  p{5cm}  p{2cm} }
	\toprule
	\textbf{Work} & \textbf{Deep Learning} & \textbf{Machine Learning} & \textbf{Data\linebreak Augmentation} & \textbf{Feature Extractor} & \textbf{Data Set} & \textbf{Result}\\
	\midrule
	\cite{03358} & Classify & & x & & HAM10000 & 0.93 (ACC)\\
	\midrule
	\cite{03798} & Classify & Classify & x & x & HAM10000 & 0.9 (ACC)\\
	\midrule
	\cite{10348} & Classify & Classify & x & & HAM10000, $PH^2$ & \\
	\midrule
	\cite{09418} & Classify & & x & & HAM10000 & 0.88 (ACC)\\
	\midrule
	\cite{01284} & Classify & & x & & HAM10000 & 0.86 (ACC)\\
	\midrule
	\cite{06612} & Classify & & x & x & HAM10000, BCN-20000, MSK & 0.85 (ACC)\\
	\midrule
	\cite{03225} & Classify & & x & & HAM10000 & 0.85 (ACC)\\
	\midrule
	\cite{12602} & Classify & & x & & HAM10000 & 0.92 (AUC)\\
	\midrule
	\cite{03426} & Classify & & x & & HAM10000 & 0.92 (AUC)\\
	\midrule
	\cite{03910} & Classify & & x & & HAM10000 & 0.74 (recall)\\
	\midrule
	\cite{05045} & & Classify & x & x & HAM10000 & \\
	\midrule
	\cite{2101.133} & Classify&  & x &  & HAM10000 & 0.92 (ACC)\\
	\midrule
	\cite{22750} & Seg&  &  &  & HAM10000 & 0.99 (ACC)\\
	\midrule
	\cite{9445180} & Seg &  &  &  & HAM10000 & 0.97 (ACC)\\
	\bottomrule
\end{tabular}
\end{adjustwidth}
		\end{table}
		\subsubsection{Deep Learning Approach}
		In Deep Learning, one of the most cutting-edge technologies  used is Soft-Attention, as stated in~\mbox{\cite{03358}}. Soumyyak~et~al. constructed several models formed by a combination of a backbone model including DenseNet201~\mbox{\cite{06993}}, InceptionResNetV2~\mbox{\cite{00567}}, ResNet50~\mbox{\cite{03385,05027}}, VGG16~\mbox{\cite{1556}} and Soft-Attention layer. Their approach adds the Soft-Attention layer at the end or the middle of the backbone model. For ResNet50 and VGG16, the Soft-Attention layer is added after the third residual block and CNN block, respectively. DenseNet201 and InceptionResNetV2 then concatenate with  Soft-Attention before a fully-connected layer and then soft-max layer. Soumyyak~et~al.'s proposed method gained great performances and also outperformed many other studies with an accuracy of 0.93 and a precision of 0.92. However, using  data augmentation on an imbalanced dataset resulted in subpar classification  classify with respect to the  classes; therefore, their model obtained a  recall and f1-score of 0.71 and 0.75, respectively. In this research, our proposed method also considers this problem and solves it.

		Using the above-mentioned backbones has been attempted previously. Rishu Garg~et~al.~\mbox{\cite{03798}} used a transfer learning approach with a CNN-based model: ResNet50 and VGG1,6 which are pretrained with an ImageNet data set. In addition, they also use data augmentation to avoid an imbalance occuring in  the dataset. Histogram equalization is also used to increase the contrast of  skin lesions before being fed into machine learning algorithms including Random Forest, XGBoost, and Support Vector Machine.	Histogram equalization can be considered as a heat map that takes the main feature as the number of occurrences of the same value pixel. This approach also gain great performances with an accuracy of 0.90 and  precision of 0.88. However, this approach can be biased since only one skin image of the dataset contains the skin lesion at the center and the background skin, and the histogram may treat the background with increased numbers of occurrence with respect to the same pixel value. In this research study, our proposed method used  Soft-Attention, which can create a heat map feature of the lesion. Otherwise, Rishu Garg~et~al.'s proposed method also faced the problem of imbalanced classification due to an imbalanced dataset with the f1-score and recall at 0.77 and 0.74, respectively.

		Instead of using the entire imbalanced data set, Abayomi-alli~et~al. decided to separate the dataset into two subsets: one contains only melanoma and the other one contains the rest~\mbox{\cite{2101.133}}. Before feeding the data to classify  melanoma, training data are then augmented by the SMOTE method. SMOTE creates artificial instances by oversampling the minority class. SMOTE recognizes k-minority class neighbors that are near  each minority class sample by using the covariance matrix. This approach obtained an accuracy, recall, and f1-score of 0.92, 0.87, and 0.82, respectively.

		Amirreaza~et~al.~\mbox{\cite{10348}} did not only use the backbone model mentioned above but also used the InceptionV3~\mbox{\cite{00567}} model. In this research study,  datasets HAM10000 and $PH^2$ are combined to create an eight-class dataset. Before being fed into  Deep CNN models, the image was resized to (224, 224) for DenseNet201, ResNet152, InceptionResNetV2, and (229, 229) for InceptionV3. The best ROC AUC values for melanoma and basal cell carcinoma are 0.94 (ResNet152) and 0.93 (DenseNet201).

@@

		\hl{Another state-of-the-art method is GradCam and Kernel SHAP~\mbox{\cite{06612}}. Kyle Young~et~al. created an agnostic model, which includes local interpretable methods that can highlight pixels that the trained network deems relevant for the final classification. In that research study, they used three datasets containing HAM10000, BCN-20000, and MSK. Before feeding into the models,  images are preprocessed by binarization with a very low threshold to find the center of mass. This approach obtained an  AUC score of 0.85.} %Please check if meaning is retained. %H.K.D Fine

		On the other hand, there are also many state-of-the-art methods with great performance on skin lesion classification. The Student-and-Teacher Model is also a high-performance model introduced in 2021~\mbox{\cite{03225}}, and it is created by Xiaohan Xing~et~al. as a combination of two models that share  memories with the other model. Therefore, the models can take full advantage of what others learn. The Student-and-Teacher model obtained an accuracy of 0.85; however, the precision and f1-score are quite low, resulting in a value of 0.76.

		SkinLinkNet~\mbox{\cite{12602}} and WonderM~\mbox{\cite{03426}} are both tested the effect of segmentation on skin lesion classification problems created by Amirreza~et~al. and Yeong Chan~et~al., respectively. In WonderM, the method used is to pad the image so that the image has an increase in shape  from (450, 600) to (600, 600). In SkinLinkNet,  the image is instead resized down to (448, 448). Both  SkinLinkNet and WonderM used UNet to perform the segmentation task, although they used EfficientNetB0 and DenseNet to perform the classification task. This approach obtained an AUC score of 0.92.

		Another approach is to use metadata, including gender, age, and capturing positions, as stated in~\mbox{\cite{03910}} by Nil Gessert~et~al.  Metadata are fed into a fully connected neural network after  encoded into a one-hot vector. All missing data points with respect to age are set to 0. To overcome the missing data problem, the research study applied one-hot encoding to the group, but the initial validation resulted in poor performance then when numerical encoding was applied. The metadata are then fed into two block networks, each one containing a Dense Layer, Batch Normalization, am ReLU activation function, and a Dropout. After all the feature vectors were extracted, the image was then concatenated with the feature vector extracted from metadata. Otherwise,  data augmentation was also applied. This approach obtained a  recall score of 0.74. The low recall score may be due to the imbalanced data set.

		Abnormal, skin lesion segmentation, on the other hand, also plays an important role in skin lesion classification. Nawaz~et~al. created a framework for Melanoma segmentation~\mbox{\cite{22750}}. Their proposed method is a Unet model but used  densenet77 as the  backbone, and all residual blocks were changed into dense block, which contains a sequence of Convolution and  Average Pooling. This melanoma segmentation approach obtain an accuracy of 0.99. Kadry~et~al. used a Unet model with a VGG deep convolution layer by pooling on the skip connection. This approach can completely extract the entire lesion, although there was an overlap observed with hair. This approach obtained an  accuracy of 0.97.

@@

	\begin{itemize}
	\item[-] Backbone model including DenseNet201, InceptionResNetV2, ResNet50/152, NasNetLarge, NasNetMobile, and MobileNetV2/V3;
	\item[-] Using metadata including age, gender, localization as another input of the model;
	\item[-] Using Soft-Attention as a feature extractor of the model;
	\item[-] A new weight loss function.
	\end{itemize}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{Materials and Methods}
	\subsection{Materials}
	\subsubsection{Image Data}
	The data set used in this paper is the HAM10000 data set published by the Havard University Dataverse \cite{10417}. There are a total of 7 classes in this data set containing Actinic keratoses and intraepithelial carcinoma or Bowen's disease (AKIEC), basal cell carcinoma (BCC),  benign keratosis-like lesions (solar lentigines / seborrheic keratoses andchen-planus like keratoses, BKL), dermatofibroma (DF), melanoma (MEL), melanocytic nevi (NV), and vascular lesions (angiomas, angiokeratomas, pyogenic granulomas and hemorrhage, VASC). The distribution of the data set is shown in the Table \ref{table:data-distribution} below:

	\begin{table}[H]
		\caption{Data Distribution in HAM10000.}
		\label{table:data-distribution}
		\setlength{\tabcolsep}{3.05mm}\begin{tabular}{c c c c c c c c c} 
\toprule
\textbf{Class} & \textbf{AKIEC} & \textbf{BCC} & \textbf{BKL} & \textbf{DF} & \textbf{MEL} & \textbf{NV} & \textbf{VASC} & \textbf{Total} \\ 
\midrule
No. Sample & 327 & 514 & 1099 & 115 & 1113 & 6705 & 142 & 10,015 \\
\bottomrule
		\end{tabular}
	\end{table}

	More than 50\% of lesions are confirmed through histopathology (HISTO); the ground truth for the rest of the cases is either follow-up examination (FOLLOWUP), expert consensus (CONSENSUS), or confirmation by in vivo confocal microscopy (CONFOCAL). On the other hand, before being used for training, the whole data are shuffled and then split into two parts. Here, $90$\% and $10$\% of the data is used for training and validating respectively. Images \hl{(See Figure \mbox{\ref{fig:data-sample}})} in this data set have the type of $RGB$ and shape of (450, 600). However, each backbone needs the different input sizes of images as well as the range of pixel value.
	\begin{figure}[H]
		\includegraphics[width=1\linewidth]{Definitions/DataDistribution}
		\caption{\hl{Example} %MDPI: 1. Please cite the figure in the text and ensure the first citation of each figure appears in numerical order. 2. Please confirm if the vertical line is necessary, if not, please remove it.
		% H.K.D We have provied the citation to the Figure 1 and feel the current version of vertical line quite great
 image of each class.}
		\label{fig:data-sample}
	\end{figure}

@@

	\begin{figure}[H]
		\includegraphics[width=0.8\linewidth]{Definitions/MainModel - Model Form}
		\caption{Overall Model Architecture.}
		\label{fig:main-model}
	\end{figure}

@@

	\begin{figure}[H]
		\includegraphics[width=0.7\linewidth]{Definitions/Model Structure}
		\caption{\hl{Overall Original} %MDPI: Please revise the "x" into a multiplication sign ("\times" U+00D7) % H.K.D confirm
 Model Architecture. This figure show the overall structure of the backbone model (non mobile-based model) including DenseNet201, InceptionResNetV2, ResNet50, ResNet152, and NasNetLarge. The detailed structure and information can be found in the Appendix \ref{appendix-table:detailed structure model}.}
		\label{fig:model-structure}
	\end{figure}

	Figure \ref{fig:mobile-model-structure}, on the other hand, shows the detailed structure of the mobile-based mobile and its combination with Soft-Attention. All of the MobileNet versions combine with the Soft-Attention module by replacing the two last convolution layers 1 \hl{$\times$} %MDPI: We revised the "x" into a multiplication sign ("\times" U+00D7). Please confirm.
 1 with the Soft-Attention module. The NasNetMobile, otherwise, combines with the Soft-Attention module by replacing the last normal cell. 
	\begin{figure}[H]
		\includegraphics[width=1\linewidth]{Definitions/Mobile Model Structure}
		\caption{\hl{Overall mobile-based} %MDPI: Please revise the "x" into a multiplication sign ("\times" U+00D7) H.K.D confirm
 model architecture. This figure shows the overall structure of the mobile-based backbone model including MobileNetV2, MobileNetV3Small, MobileNetV3Large, and NasNetMobile. The detailed structure and information can be found in the Appendix \ref{appendix-table:detailed mobile model structure}.}
		\label{fig:mobile-model-structure}
	\end{figure}

@@

	\begin{figure}[H]
		\includegraphics[width=1\linewidth]{"Definitions/Input Schema"}
		\caption{Input Schema.}
		\label{fig:input-schema}
	\end{figure}

	\subsubsection{Backbone Model}
	In this paper, the backbone models used in this paper are DenseNet201 \cite{06993}, Inception~\cite{00567}, MobileNets \cite{04861,04381,02244}, ResNet \cite{03385,05027}, and NasNet \cite{07012}. The combination of DenseNet201, InceptionResNetV2, and the Soft-Attention layer are both tested by the previous paper \cite{03358} with a great performance. Otherwise, Resnet50 also well classifies but with much fewer number of parameters and less depth than based on its f1-score and precision stated. Therefore, in this paper, the performance of the model Resnet152 and NasnetLarge models, which have more parameters and depth, is analyzed. On the other hand, three versions of MobileNet and the NasnetMobile will also be analyzed, which has fewer parameters \hl{(see Figure \mbox{\ref{table:model-summary}})} and depth.

	\begin{table}[H]
		\caption{\hl{Size} %MDPI: 1. Please cite the table in the text and ensure the first citation of each table appears in numerical order. 2. We remove the vertical line, please confirm.
 , parameters, and depth of the backbone model used in this paper.}
		\label{table:model-summary}
		\setlength{\tabcolsep}{5.2mm}\begin{tabular}{l  c c c} 
\toprule
\textbf{Model} & \textbf{Size (MB)} & \textbf{No. Trainable Parameters} & \textbf{Depth} \\ 
\midrule
Resnet50 & 98 & 25,583,592 & 107 \\ 
\midrule
Resnet152 & 232 & 60,268,520 & 311 \\ 
\midrule
DenseNet201 & 80 & 20,013,928 & 402 \\
\midrule
InceptionResNetV2 & 215 & 55,813,192 & 449 \\
\midrule
MobileNetV2 & 14 & 3,504,872 & 105 \\ 
\midrule
MobileNetV3Small & Unknown & 2,542,856 & 88 \\ 
\midrule
MobileNetV3Large & Unknown & 5,483,032 & 118 \\
\midrule
NasnetMobile & 23 & 5,289,978 & 308 \\
\midrule
NasnetLarge & 343 & 88,753,150 & 533 \\ 
\bottomrule
		\end{tabular}
	\end{table}

>>>>

\address{$^{1}$ \quad \hl{School} %MDPI: we combined the same affiliation 1 and 3, please confirm.
 of Electrical and Electronic Engineering, Hanoi University of Science and Technology, \hl{Vietnam;} %MDPI: Please add the city and post code.
\hl{dung.nguyenviet1@hust.edu.vn, khoi.dh200322@sis.hust.edu.vn} %MDPI: This email address is different from the submitting system. Please confirm which one is correct. %H.K.D confirmed
\\
$^{2}$ \quad Faculty of Information Technology, University of Transport and Communications, \hl{Vietnam} %MDPI: Please add the city and post code.
}

@@

% Abstract (Do not insert blank lines, i.e. \\) s
\abstract{Today, the rapid development of industrial zones leads to an increased incidence of skin	diseases because of polluted air. According to a report by the American Cancer Society, it is estimated that in 2022 there will be about 100,000 people suffering from skin cancer and more than 7600 of these people will not survive. In the context that doctors at provincial hospitals and health facilities are overloaded, doctors at lower levels lack experience, and having	a tool to support doctors in the process of diagnosing skin diseases quickly and accurately is essential. Along with the strong development of artificial intelligence technologies, many solutions to support the diagnosis of skin diseases have been researched and developed. In this paper, a combination of one Deep Learning model (DenseNet, InceptionNet, ResNet, etc) with Soft-Attention, which unsupervisedly extract a heat map of main skin lesions. Furthermore, personal information including age and gender are also used. It is worth noting that a new loss function that takes into account the data imbalance is also proposed. Experimental results on data set HAM10000 show that using InceptionResNetV2 with Soft-Attention and the new loss function gives 90 percent accuracy, mean of precision, F1-score, recall, and AUC of 0.81, 0.81, 0.82, and 0.99, respectively. Besides, using MobileNetV3Large combined with Soft-Attention and the new loss function, even though the number of parameters is 11~times less and the number of hidden layers is 4 times less, it achieves an accuracy of 0.86 and 30 times faster diagnosis than InceptionResNetV2.}

@@

	To adapt the rise in skin cancer cases, AI algorithms over the last decade has a great performance. Some typical models that can be mentioned are DenseNet \cite{06993}, EfficientNet~\cite{04861}, Inception \cite{00567,07261}, MobileNets\cite{04861,04381,02244}, \hl{Xception\mbox{\cite{02357}}}, ResNet \cite{03385,05027}, and NasNet \cite{07012}. Some of these models which have been used as a backbone model in this paper will be discussed in the Related Work section.

@@

	{Skin lesion classification is not a new area, since there are many great performance models constructed, recent years. The skin classification approaches can be divided into two main approaches: Deep Learning and Machine Learning (\hl{\mbox{as shown in Table \ref{table:related-work-summary}}}). Both approaches gain great performance. Data Augmentation and Feature Extractor, otherwise are two main supporters that make the model better. %H.K.D We provided the citation to Table 1
		\begin{table}[H]
\caption{\hl{Summary of related} %MDPI: we updated the format of all tables, please confirm the change. Please cite the table in the text and ensure the first citation of each table appears in numerical order. %H.K.D We also changed the table caption
works.}
\label{table:related-work-summary}

\begin{adjustwidth}{-\extralength}{0cm}
%\centering %% If there is a figure in wide page, please release command \centering
\centering
\begin{tabular}{ c  p{1.8cm}  p{1.8cm}  p{2.55cm}  p{1.5cm}  p{5cm}  p{2cm} }
	\toprule
	\textbf{Work} & \textbf{Deep Learning} & \textbf{Machine Learning} & \textbf{Data\linebreak Augmentation} & \textbf{Feature Extractor} & \textbf{Data Set} & \textbf{Result}\\
	\midrule
	\cite{03358} & Classify & & x & & HAM10000 & 0.93 (ACC)\\
	\midrule
	\cite{03798} & Classify & Classify & x & x & HAM10000 & 0.9 (ACC)\\
	\midrule
	\cite{10348} & Classify & Classify & x & & HAM10000, $PH^2$ & \\
	\midrule
	\cite{09418} & Classify & & x & & HAM10000 & 0.88 (ACC)\\
	\midrule
	\cite{01284} & Classify & & x & & HAM10000 & 0.86 (ACC)\\
	\midrule
	\cite{06612} & Classify & & x & x & HAM10000, BCN-20000, MSK & 0.85 (ACC)\\
	\midrule
	\cite{03225} & Classify & & x & & HAM10000 & 0.85 (ACC)\\
	\midrule
	\cite{12602} & Classify & & x & & HAM10000 & 0.92 (AUC)\\
	\midrule
	\cite{03426} & Classify & & x & & HAM10000 & 0.92 (AUC)\\
	\midrule
	\cite{03910} & Classify & & x & & HAM10000 & 0.74 (recall)\\
	\midrule
	\cite{05045} & & Classify & x & x & HAM10000 & \\
	\midrule
	\cite{2101.133} & Classify&  & x &  & HAM10000 & 0.92 (ACC)\\
	\midrule
	\cite{22750} & Seg&  &  &  & HAM10000 & 0.99 (ACC)\\
	\midrule
	\cite{9445180} & Seg &  &  &  & HAM10000 & 0.97 (ACC)\\
	\bottomrule
\end{tabular}
\end{adjustwidth}
		\end{table}
		\subsubsection{Deep Learning Approach}
		In Deep Learning, one of the most cutting-edge technologies  used is Soft-Attention, as stated in~\mbox{\cite{03358}}. Soumyyak~et~al. constructed several models formed by a combination of a backbone model including DenseNet201~\mbox{\cite{06993}}, InceptionResNetV2~\mbox{\cite{00567}}, ResNet50~\mbox{\cite{03385,05027}}, VGG16~\mbox{\cite{1556}} and Soft-Attention layer. Their approach adds the Soft-Attention layer at the end or the middle of the backbone model. For ResNet50 and VGG16, the Soft-Attention layer is added after the third residual block and CNN block, respectively. DenseNet201 and InceptionResNetV2 then concatenate with  Soft-Attention before a fully-connected layer and then soft-max layer. Soumyyak~et~al.'s proposed method gained great performances and also outperformed many other studies with an accuracy of 0.93 and a precision of 0.92. However, using  data augmentation on an imbalanced dataset resulted in subpar classification  classify with respect to the  classes; therefore, their model obtained a  recall and F1-score of 0.71 and 0.75, respectively. In this research, our proposed method also considers this problem and solves it.

		Using the above-mentioned backbones has been attempted previously. Rishu Garg~et~al. \mbox{\cite{03798}} used a transfer learning approach with a CNN-based model: ResNet50 and VGG16 which are pretrained with an ImageNet data set. In addition, they also use data augmentation to avoid an imbalance occurring in  the data set. Histogram equalization is also used to increase the contrast of  skin lesions before being fed into machine learning algorithms including Random Forest, XGBoost, and Support Vector Machine. Histogram equalization can be considered as a heat map that takes the main feature as the number of occurrences of the same value pixel. This approach also gain great performances with an accuracy of 0.90 and  precision of 0.88. However, this approach can be biased since only one skin image of the dataset contains the skin lesion at the center and the background skin, and the histogram may treat the background with increased numbers of occurrence with respect to the same pixel value. In this research study, our proposed method used  Soft-Attention, which can create a heat map feature of the lesion. Otherwise, Rishu Garg~et~al.'s proposed method also faced the problem of imbalanced classification due to an imbalanced dataset with the F1-score and recall at 0.77 and 0.74, respectively.

		Instead of using the entire imbalanced data set, Abayomi-alli~et~al. decided to separate the dataset into two subsets: one contains only melanoma and the other one contains the rest~\mbox{\cite{2101.133}}. Before feeding the data to classify  melanoma, training data are then augmented by the SMOTE method. SMOTE creates artificial instances by oversampling the minority class. SMOTE recognizes k-minority class neighbors that are near  each minority class sample by using the covariance matrix. This approach obtained an accuracy, recall, and F1-score of 0.92, 0.87, and 0.82, respectively.

		Amirreaza~et~al.~\mbox{\cite{10348}} did not only use the backbone model mentioned above but also used the InceptionV3~\mbox{\cite{00567}} model. In this research study,  datasets HAM10000 and $PH^2$ are combined to create an eight-class dataset. Before being fed into  Deep CNN models, the image was resized to (224, 224) for DenseNet201, ResNet152, InceptionResNetV2, and (229, 229) for InceptionV3. The best AUC values for melanoma and basal cell carcinoma are 0.94 (ResNet152) and 0.93 (DenseNet201).

@@

		\hl{Another state-of-the-art method is GradCam and Kernel SHAP~\mbox{\cite{06612}}. Kyle Young~et~al. created an agnostic model, which includes local interpretable methods that can highlight pixels that the trained network deems relevant for the final classification. In that research study, they used three datasets containing HAM10000, BCN-20000, and MSK. Before feeding into the models,  images are preprocessed by binarization with a very low threshold to find the center of mass. This approach obtained an  AUC of 0.85.} %Please check if meaning is retained. %V.D.N confirmed

		On the other hand, there are also many state-of-the-art methods with great performance on skin lesion classification. The Student-and-Teacher Model is also a high-performance model introduced in 2021~\mbox{\cite{03225}}, and it is created by Xiaohan Xing~et~al. as a combination of two models that share  memories with the other model. Therefore, the models can take full advantage of what others learn. The Student-and-Teacher model obtained an accuracy of 0.85; however, the precision and F1-score are quite low, resulting in a value of 0.76.

		SkinLinkNet~\mbox{\cite{12602}} and WonderM~\mbox{\cite{03426}} are both tested the effect of segmentation on skin lesion classification problems created by Amirreza~et~al. and Yeong Chan~et~al., respectively. In WonderM, the method used is to pad the image so that the image has an increase in shape  from (450, 600) to (600, 600). In SkinLinkNet,  the image is instead resized down to (448, 448). Both  SkinLinkNet and WonderM used UNet to perform the segmentation task, although they used EfficientNetB0 and DenseNet to perform the classification task. This approach obtained an AUC of 0.92.

		Another approach is to use metadata, including gender, age, and capturing positions, as stated in~\mbox{\cite{03910}} by Nil Gessert~et~al.  Metadata are fed into a fully connected neural network after  encoded into a one-hot vector. All missing data points with respect to age are set to 0. To overcome the missing data problem, the research study applied one-hot encoding to the group, but the initial validation resulted in poor performance then when numerical encoding was applied. The metadata are then fed into two block networks, each one containing a Dense Layer, Batch Normalization, am ReLU activation function, and a Dropout. After all the feature vectors were extracted, the image was then concatenated with the feature vector extracted from metadata. Otherwise,  data augmentation was also applied. This approach obtained a  recall of 0.74. The low recall may be due to the imbalanced data set.

		Abnormal, skin lesion segmentation, on the other hand, also plays an important role in skin lesion classification. Nawaz~et~al. created a framework for Melanoma segmentation~\mbox{\cite{22750}}. Their proposed method is a Unet model but used  DenseNet77 as the  backbone, and all residual blocks were changed into dense block, which contains a sequence of Convolution and  Average Pooling. This melanoma segmentation approach obtain an accuracy of 0.99. Kadry~et~al. used a Unet model with a VGG deep convolution layer by pooling on the skip connection. This approach can completely extract the entire lesion, although there was an overlap observed with hair. This approach obtained an  accuracy of 0.97.

@@

	\begin{itemize}
	\item[-] Backbone model including DenseNet201, InceptionResNetV2, ResNet50/152, NasNetLarge, NasNetMobile, and MobileNetV2/V3;
	\item[-] Using metadata including age, gender, localization as another input of the model;
	\item[-] Using Soft-Attention as a feature extractor of the model;
	\item[-] A new weight loss function.
	\end{itemize}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{Materials and Methods}
	\subsection{Materials}
	\subsubsection{Image Data}
	The data set used in this paper is the HAM10000 data set published by the Havard University Dataverse \cite{10417}. There are a total of 7 classes in this data set containing Actinic keratoses and intraepithelial carcinoma or Bowen's disease (AKIEC), basal cell carcinoma (BCC),  benign keratosis-like lesions (solar lentigines / seborrheic keratoses andchen-planus like keratoses, BKL), dermatofibroma (DF), melanoma (MEL), melanocytic nevi (NV), and vascular lesions (angiomas, angiokeratomas, pyogenic granulomas and hemorrhage, VASC). The distribution of the data set is shown in Table \ref{table:data-distribution} below:

	\begin{table}[H]
		\caption{Data distribution in HAM10000.}
		\label{table:data-distribution}
		\setlength{\tabcolsep}{3.05mm}\begin{tabular}{c c c c c c c c c} 
\toprule
\textbf{Class} & \textbf{AKIEC} & \textbf{BCC} & \textbf{BKL} & \textbf{DF} & \textbf{MEL} & \textbf{NV} & \textbf{VASC} & \textbf{Total} \\ 
\midrule
No. Sample & 327 & 514 & 1099 & 115 & 1113 & 6705 & 142 & 10,015 \\
\bottomrule
		\end{tabular}
	\end{table}

	More than 50\% of lesions are confirmed through histopathology (HISTO); the ground truth for the rest of the cases is either follow-up examination (FOLLOWUP), expert consensus (CONSENSUS), or confirmation by in vivo confocal microscopy (CONFOCAL). On the other hand, before being used for training, the whole data are shuffled and then split into two parts. Here, $90$\% and $10$\% of the data is used for training and validating respectively. Images in this data set have the type of $RGB$ and shape of (450, 600). However, each backbone needs the different input sizes of images as well as the range of pixel value \hl{(as shown in Figure \mbox{\ref{fig:data-sample}})}.
	\begin{figure}[H]
		\includegraphics[width=0.8\linewidth]{Definitions/DataDistribution}
		\caption{\hl{Example} %MDPI: 1. Please cite the figure in the text and ensure the first citation of each figure appears in numerical order. 2. Please confirm if the vertical line is necessary, if not, please remove it.
		% H.K.D We have provied the citation to the Figure 1 and feel the current version of vertical line quite great
 image of each class.}
		\label{fig:data-sample}
	\end{figure}

@@

	\begin{figure}[H]
		\includegraphics[width=0.9\linewidth]{Definitions/MainModel - Model Form}
		\caption{Overall model architecture.}
		\label{fig:main-model}
	\end{figure}

@@

	\begin{figure}[H]
		\includegraphics[width=0.9\linewidth]{Definitions/Model Structure}
		\caption{\hl{Proposed} %MDPI: Please revise the "x" into a multiplication sign ("\times" U+00D7) % H.K.D confirm. %H.K.D confirmed
 backbone model architecture. This figure show the overall structure of the backbone model (non mobile-based model) including DenseNet201, InceptionResNetV2, ResNet50, ResNet152, and NasNetLarge \hl{with Soft-Attention}. The detailed structure and information can be found in the Appendix \ref{appendix-table:detailed structure model}.}
		\label{fig:model-structure}
	\end{figure}

	Figure \ref{fig:mobile-model-structure}, on the other hand, shows the detailed structure of the mobile-based mobile and its combination with Soft-Attention. All of the MobileNet versions combine with the Soft-Attention module by replacing the two last convolution layers 1 \hl{$\times$} %MDPI: We revised the "x" into a multiplication sign ("\times" U+00D7). Please confirm.
 1 with the Soft-Attention module. The NasNetMobile, otherwise, combines with the Soft-Attention module by replacing the last normal cell. 
	\begin{figure}[H]
		\includegraphics[width=0.9\linewidth]{Definitions/Mobile Model Structure}
		\caption{\hl{Mobile-based} %MDPI: Please revise the "x" into a multiplication sign ("\times" U+00D7) H.K.D confirm
 backbone model architecture. This figure shows the overall structure of the mobile-based backbone model including MobileNetV2, MobileNetV3Small, MobileNetV3Large, and NasNetMobile. The detailed structure and information can be found in the Appendix \ref{appendix-table:detailed mobile model structure}.}
		\label{fig:mobile-model-structure}
	\end{figure}

@@

	\begin{figure}[H]
		\includegraphics[width=1\linewidth]{"Definitions/Input Schema"}
		\caption{Input schema.}
		\label{fig:input-schema}
	\end{figure}

	\subsubsection{Backbone Model}
	In this paper, the backbone models used in this paper are DenseNet201 \cite{06993}, Inception~\cite{00567}, MobileNets \cite{04861,04381,02244}, ResNet \cite{03385,05027}, and NasNet \cite{07012}. The combination of DenseNet201, InceptionResNetV2, and the Soft-Attention layer are both tested by the previous paper \cite{03358} with a great performance. Otherwise, Resnet50 also well classifies but with much fewer number of parameters and less depth than based on its F1-score and precision stated. Therefore, in this paper, the performance of the model Resnet152 and NasnetLarge models, which have more parameters and depth, is analyzed. On the other hand, three versions of MobileNet and the NasnetMobile will also be analyzed, which has fewer parameters \hl{(as shown in Table \mbox{\ref{table:model-summary}})} and depth.

	\begin{table}[H]
		\caption{\hl{Size}, parameters, and depth of the backbone model used in this paper.}%MDPI: 1. Please cite the table in the text and ensure the first citation of each table appears in numerical order. 2. We remove the vertical line, please confirm.
		%V.D.N confirmed
		\label{table:model-summary}
		\setlength{\tabcolsep}{5.2mm}\begin{tabular}{l  c c c} 
\toprule
\textbf{Model} & \textbf{Size (MB)} & \textbf{No. Trainable Parameters} & \textbf{Depth} \\ 
\midrule
Resnet50 & 98 & 25,583,592 & 107 \\ 
\midrule
Resnet152 & 232 & 60,268,520 & 311 \\ 
\midrule
DenseNet201 & 80 & 20,013,928 & 402 \\
\midrule
InceptionResNetV2 & 215 & 55,813,192 & 449 \\
\midrule
MobileNetV2 & 14 & 3,504,872 & 105 \\ 
\midrule
MobileNetV3Small & Unknown & 2,542,856 & 88 \\ 
\midrule
MobileNetV3Large & Unknown & 5,483,032 & 118 \\
\midrule
NasnetMobile & 23 & 5,289,978 & 308 \\
\midrule
NasnetLarge & 343 & 88,753,150 & 533 \\ 
\bottomrule
		\end{tabular}
	\end{table}
